---
title: "Carly_Assignment4"
output: html_notebook
---
#Install Packages
```{r}
install.packages("tidyverse", dependencies = TRUE)
install.packages("ggthemes", dependencies = TRUE)

```

#Load Packages(2)
```{r}
library(tidyverse)
library(ggthemes)
```

#Import Data(3)
```{r}
assignment4 = read_csv("a4_data.csv")
```

#Rows and Columns (4)
```{r}
nrow(assignment4)
ncol(assignment4)
#The data file has 3700 rows and 12 columns
```

#Unique participants and trials(5)
```{r}
#trial1 = assignment4 %>% filter(trial==1)
#nrow(trial1)
#there were 37 unique subjects

assignment4 %>% group_by(subject)%>%count()
#each subject completed 100 trials

```

#Levels of Variables
```{r}
assignment4 = assignment4%>%mutate(prime_condition = as.factor(prime_condition), state=as.factor(state))

levels(assignment4%>%pull(prime_condition))
levels(assignment4%>%pull(state))

#the variable "prime condition" has four levels. The variable "state" also has four levels

```

#Subsets of Columns(7)
```{r}
prime_information = assignment4 %>% select(subject,prime_condition)
```

#Subsets of Rows(8)
```{r}
phonological = assignment4%>%filter(prime_condition =="phonological", accuracy == 1)
```

#Summarizing accuracy per subject(9)
```{r}
subject_acc = assignment4 %>% group_by(subject) %>% summarise(mean_acc = mean(accuracy))
```

#Summarizing accuracy per prime condition(10)
```{r}
prime_acc = assignment4 %>% group_by(prime_condition) %>% summarise(mean_acc = mean(accuracy), sd_acc = sd(accuracy))
```

#Histogram of Subject Accuracy(11)
```{r}
subject_acc %>% ggplot(aes(x=mean_acc)) +
  geom_histogram(binwidth = 0.2, fill = "brown", color = "black") +
  xlab ("mean accuracy")+ 
  ylab ("count")+ 
  ggtitle("Histogram of mean accuracy")
```

#Bar plot of Prime Condition (12)
```{r}
prime_acc %>% 
  ggplot(aes(x = prime_condition, y = mean_acc)) +
  geom_bar (stat = "identity", fill = "pink", color = "purple")
  theme_fivethirtyeight()+
  xlab ("prime condition") +
  ylab ("mean accuracy") +
  ggtitle("Mean accuracy across prime condition")
```

#Data Interpretation (13)
```{r}

```

EXTRA CREDIT

#Summarizing accuracy per prime condition and state (14)
```{r}
state_prime_acc = assignment4%>%group_by(state, prime_condition)%>%summarize(mean_acc = mean(accuracy))
```

#Bar plot of prime condition and state
```{r}
state_prime_acc %>% 
  ggplot(aes(x = prime_condition, y = mean_acc, fill = state)) +
  geom_col(position = "dodge") +
  theme_few() +
  xlab ("prime condition") +
  ylab("mean accuaracy") +
  ggtitle("mean accuracy across prime condiiton and state")
```

